INTELLIGENT SYSTEMS

### 2021-04-22 slides/slides_paper7.tex
some update
some fixes

\begin{frame}{RELATED WORK - What types of image noise?}
    The noises analyzed in this paper are mainly two categories of Gaussian 
    noises:
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{block}{GAUSSIAN MIXED-NOISE}
                $$
                \small
                n = \left\{
                    \begin{array}{cc}
                        n_1, & with~probability~r_1\\
                        n_2, & with~probability~r_2\\
                        \cdots, & \cdots\\
                        n_k, & with~probability~r_k\\ 
                    \end{array}
                    \right\}
                $$
            \end{block}  
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.47\linewidth}
            \begin{block}{GAUSSIAN RANDOM NOISE}
                $$
                \small
                n = \left\{
                    \begin{array}{cc}
                        n_1, & with~probability~1-r\\
                        n_2, & with~probability~r\\
                    \end{array}
                    \right\}
                $$
            \end{block} 
        \end{minipage}
    \end{minipage}
    where $ n_k $ is the \emph{k}-th noise component with probability density function (PDF) 
    $ p_k $ and $ r_k $ are the unknown mixture ratios and thei sum is equal to 
    1. Each type of noise has a standard deviation ($\sigma$) which indicates the 
    amount of noise distribution present.     
\end{frame}

@@

\begin{frame}{EXPERIMENTAL RESULTS - Gaussian mixed-noise}
    The indexs used to estimate the quality of the restructured images are 
    the \emph{Signal-to-Noise Ratio} (PSNR) and the \emph{Structural Similarity Index} 
    (SSIM). The results obtained by comparing different methods with the 
    proposed, in image reconstruction and Gaussian mixed-noise removal, one 
    are visible in figure \ref{fig:GMNComp} and table \ref{indexCompare}. The set test images were taken from 
    the BSDS100 dataset.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.8\linewidth]{images/paper7/GMN comparison.png}
        \centering
        \caption{Image reconstruction under Gaussain mixture noise comparison.}
        \label{fig:GMNComp}
    \end{figure}

@@

    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.7\linewidth]{images/paper7/crop result.png}
        \centering
        \caption{PSNR result of different methods on cropped real noisy images.}
        \label{fig:cropRes}
    \end{figure}

>>>>

\begin{frame}{RELATED WORK - What types of image noises?}
    The noises analyzed in this paper are mainly two categories of Gaussian 
    noises:
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{block}{GAUSSIAN MIXED-NOISE}
                $$
                \small
                n = \left\{
                    \begin{array}{cc}
                        n_1, & with~probability~r_1\\
                        n_2, & with~probability~r_2\\
                        \cdots, & \cdots\\
                        n_k, & with~probability~r_k\\ 
                    \end{array}
                    \right\}
                $$
            \end{block}  
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.47\linewidth}
            \begin{block}{GAUSSIAN RANDOM NOISE}
                $$
                \small
                n = \left\{
                    \begin{array}{cc}
                        n_1, & with~probability~1-r\\
                        n_2, & with~probability~r\\
                    \end{array}
                    \right\}
                $$
            \end{block} 
        \end{minipage}
    \end{minipage}
    where $ n_k $ is the \emph{k}-th noise component with probability density function (PDF) 
    $ p_k $ and $ r_k $ are the unknown mixture ratios and their sum is equal to 
    1. Each type of noise has a standard deviation ($\sigma$) which indicates the 
    amount of noise distribution present.     
\end{frame}

@@

\begin{frame}{EXPERIMENTAL RESULTS - Gaussian mixed-noise}
    The indexs used to estimate the quality of the restructured images are 
    the \emph{Signal-to-Noise Ratio} (PSNR) and the \emph{Structural Similarity Index} 
    (SSIM). The results obtained by comparing different methods with the 
    proposed, in image reconstruction and Gaussian mixed-noise removal, one 
    are visible in figure \ref{fig:GMNComp} and table \ref{indexCompare}. The test set images were taken from 
    the BSDS100 dataset.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.8\linewidth]{images/paper7/GMN comparison.png}
        \centering
        \caption{Image reconstruction under Gaussain mixture noise comparison.}
        \label{fig:GMNComp}
    \end{figure}

@@

    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.6\linewidth]{images/paper7/crop result.png}
        \centering
        \caption{PSNR result of different methods on cropped real noisy images.}
        \label{fig:cropRes}
    \end{figure}

### 2021-04-22 slides/slides_paper8.tex
some fixes

\begin{frame}{METHODS - EMDSLT Architecture}
    The proposed framework, called Ensemble Multi Deep Stream Similarity 
    Learnining Tracking (EMDSLT), is composed of some netwroks. Those 
    in blue are fully-convolutional networks while those in red are useful for 
    re-verification and re-detection operations, responsible for recovery from 
    failures and the template updating.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/EMDSLT.png}
        \centering
        \caption{The EMDSLT framework.}
        \label{fig:EMDSLT}
    \end{figure}
\end{frame}

>>>>

\begin{frame}{METHODS - EMDSLT Architecture}
    The proposed framework, called Ensemble Multi Deep Stream Similarity 
    Learnining Tracking (EMDSLT), is composed of some networks. Those 
    in blue are fully-convolutional networks while those in red are useful for 
    re-verification and re-detection operations, responsible for recovery from 
    failures and the template updating.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/EMDSLT.png}
        \centering
        \caption{The EMDSLT framework.}
        \label{fig:EMDSLT}
    \end{figure}
\end{frame}
